---
title: "Tidyverse"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Tidyverse

In this assignment, you’ll practice collaborating around a code project with GitHub.  You could consider our collective work as building out a book of examples on how to use TidyVerse functions.

GitHub repository:  https://github.com/acatlin/FALL2020TIDYVERSE

FiveThirtyEight.com datasets.

Kaggle datasets. 

Your task here is to Create an Example.  Using one or more TidyVerse packages, and any dataset from fivethirtyeight.com or Kaggle, create a programming sample “vignette” that demonstrates how to use one or more of the capabilities of the selected TidyVerse package with your selected dataset. (25 points)


#### Read data using readr::read_csv

```{r }
library(tidyverse)

pums <- read_csv("https://raw.githubusercontent.com/szx868/data607/master/Tidyverse/2019PUMS_PERSON_DATA_NY.csv")


```
#### Using dplyr::select to have column you needed

```{r}
select(pums,c("Age","SEX","Total_Personal_Earnings","Total_Personal_Income"))

```

#### Using dplyr::filter to age

```{r}
filter(pums,Age > 36)

```

### Additional Examples

Finding those with an age less than 36 in the pums data. 

```{r}
filter(pums, Age < 36)
```


### Details 

filter() is used to subset data within a data frame. It selects the rows that satisfy a condition specified. When selecting, the function must return a result of TRUE for all rows to successfully to apply the function to all row data. Otherwise, the function will automatically drop the rows that contain NA or missing values. 


### Arguments

There are three parts to the function. It is used as follows:

```{r}
filter(.data, ..., .preserve = FALSE)
```


```{r eval=FALSE}
.data
```

The information used to run through the function. It can be a data frame, a tibble, or lazy data frame such as dbplyr, dtplyr. 


```{r eval=FALSE}
...
```

The selection criteria, expression, or condition


```{r eval=FALSE}
.preserve
```

Used for grouped data. Default is FALSE. When TRUE, the group structure is kept as is. 


